Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-03-09 Paper/paper.tex
Update text

We now consider the implications for hydrogen and helium reionization
for the ionizing photon emissivity derived above.  This requires that
we extrapolate the emissivity of Equation XX to higher redshifts.
Unfortunately, the volume emissivity in our model cannot be
extrapolated to higher redshifts.  The model of Hopkins suffered with
the same problem.  \gk{Do we need to show two cases here?  One in
  which we extrapolate the emissivity and another in which we stop
  where data end.  There is perhaps a third possibility in which use
  the current emissivity model upto where data end.}  The evolution of
the volume averaged ionized fraction of hydrogen is given by
\citep{2012ApJ...746..125H}
\begin{equation}
{dQ_\nHII\over dt}={\dot n_{\rm ion}\over \langle n_\nH \rangle} -{Q_\nHII\over
\langle t_{\rm rec}\rangle},
\label{eq:qdot}
\end{equation}
and the corresponding equation doubly ionized Helium is
\begin{equation}
{dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
\langle t_{\rm rec,He}\rangle}.
\label{eq:qHedot}
\end{equation}
We assume that the Helium is singly reionized together with hydrogen.
In order to get the 4~Ry emissivity of quasars we use the SED from
equation XX.  The recombination times are given by
\begin{equation}
\langle t_{\rm rec}\rangle=[\chi \langle n\rangle \alpha_B\,C]^{-1},
\label{eq:trec}
\end{equation}
where $n$ is the volume averaged density of hydrogen and helium,
respectively.  We assume that hydrogen and helium have similar
clumping factors, given by \citep{2015ApJ...813L...8M}
\begin{equation}
  C = 2.8\left(\frac{1+z}{6}\right)^{-1.1}.
\end{equation}
For the helium recombination coeffienct, we use the fitting function
provided by \citet{1997MNRAS.292...27H}.  For hydrogen recombination
coefficient, we use the fitting function provided by
\citet{2011piim.book.....D}.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
  \end{center}
  \caption{Helium reionization. \gk{What is La Plante's luminosity
      limit?  Why is his redshift of reionization lower than ours?
      Waiting for Puchwein to give us his model.  Do we need a table
      for Q evolution of H and He?  Should we tabulate Helium
      photoionisation rate?}}
\end{figure}

@@

% Check spellings
% Check notes for more names with add
% Something to add for Joe and Gabor?
We acknowledge useful discussions with James Aird, Manda Banerji,
Tirthankar Roy Choudhury, Xiaohui Fan, Andrea Ferrara, Martin
Haehnelt, Sergey Koposov, Richard McMahon, Ewald Puchwein, Gordon
Richards, and Alberto Rorai.  GK is supported by ERC Advanced Grant
320596 `The Emergence of Structure During the Epoch of Reionization'.

@@

In our analysis above, we did not include the 22 low-luminosity
($M_{1450}>-22.6$) AGN between redshifts $z=4.1$ and $6.3$ reported by
\citet{2015AA...578A..83G} using a novel X-ray/NIR selection
criterion.  This was because we wanted to restrict our sample to
quasars that have robust spectroscopic redshift determinations.  In
their work, \citet{2015AA...578A..83G} found a steep faint-end of the
luminosity function at these redshifts.  With this luminosity function
they obtained a large value of hydrogen ionizing emissivity that could
explain the \lya data singlehandedly.  In this section, we compare our
results with \citet{2015AA...578A..83G}.  The black points in Figure
XX show the parameters of the double power law luminosity function
when the \citet{2015AA...578A..83G} sample is added to our analysis.
The parameter values do not change significantly.  The
\citet{2015AA...578A..83G} sample is thus consistent with the double
power law luminosity function preferred by other data at comparable
redshifts.  However, as we see in Figure XX, the total emissivity in
our model is still significantly lower than that obtained by
\citet{2015AA...578A..83G}.  Figure XX provides an explanation for
this. The double power law fits favoured by \citet{2015AA...578A..83G}
are quite different from our fits.  The character luminosity $M_*$
favoured by \citet{2015AA...578A..83G} is much fainter ($\sim -23$ at
$z = 5$) than that resulting out of our analysis ($\sim -29$ at $z =
5$).  Figure XX suggests that this is because of the SDSS Stripe 82
data \gk{citation} and because \citet{2015AA...578A..83G} ignore the
Kashikawa and Willott samples \gk{citation}.  It is possible that our
corrections to the Glikman data \gk{citation} also plays a role in
this.  In sum, the differnce in our emissivities is not due to lack of
faint quasars but because of the difference with Giallongo at
intermediate luminosities.

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_g.pdf}
  \end{center}
  \caption{Effect of including Giallongo qsos in our analysis.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{giallongo_compare.pdf}
  \end{center}
  \caption{Comparison of our LFs with Giallongo's LFs.}
\end{figure*}

@@

We make the homogenised quasar data and the code developing and
analysing luminosity function models available at
\url{https://github.com/gkulkarni/QLF} under the MIT open source
software license.  \gk{Remember to make URL public and set appropriate
  license upon publication of paper.}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
  \end{center}
  \caption{Evolution of the \HeIII\ ionization fraction in our model,
    when the qso luminosity function is integrated down to
    $M_{1450}=-21$ (black curve) and when it is extrapolated and
    integrated down to $M_{1450}=-18$ (brown curve).  Other curves
    show models of \citet[solid grey]{2012ApJ...746..125H},
    \citet[dashed grey]{2015ApJ...813L...8M}, \citet[light blue and
      shaded region]{2016ApJ...828...90L},
    \citet[blue]{2018arXiv180104931P}. \gk{Do we need to add any more
      models from literature?}}
\end{figure}

We now consider the implications for hydrogen and helium reionization
for the ionizing photon emissivity derived above.  This requires that
we extrapolate the emissivity of Equation XX to higher redshifts.
Unfortunately, the volume emissivity in our model cannot be
extrapolated to higher redshifts.  The model of Hopkins suffered with
the same problem.  \gk{Do we need to show two cases here?  One in
  which we extrapolate the emissivity and another in which we stop
  where data end.  There is perhaps a third possibility in which use
  the current emissivity model upto where data end.}  The evolution of
the volume averaged ionized fraction of hydrogen is given by \gk{Is
  this really volume-weighted?}  \citep{2012ApJ...746..125H}
\begin{equation}
{dQ_\nHII\over dt}={\dot n_{\rm ion}\over \langle n_\nH \rangle} -{Q_\nHII\over
\langle t_{\rm rec}\rangle},
\label{eq:qdot}
\end{equation}
and the corresponding equation doubly ionized Helium is
\begin{equation}
{dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
\langle t_{\rm rec,He}\rangle}.
\label{eq:qHedot}
\end{equation}
We assume that the Helium is singly reionized together with hydrogen.
In order to get the 4~Ry emissivity of quasars we use the SED from
equation XX.  The recombination times are given by
\begin{equation}
\langle t_{\rm rec}\rangle=[\chi \langle n\rangle \alpha_B\,C]^{-1},
\label{eq:trec}
\end{equation}
where $n$ is the volume averaged density of hydrogen and helium,
respectively.  We assume that hydrogen and helium have similar
clumping factors, given by \citep{2015ApJ...813L...8M}
\begin{equation}
  C = 2.8\left(\frac{1+z}{6}\right)^{-1.1}.
\end{equation}
For the helium recombination coeffienct, we use the fitting function
provided by \citet{1997MNRAS.292...27H}.  For hydrogen recombination
coefficient, we use the fitting function provided by
\citet{2011piim.book.....D}.

@@

@@

It is a pleasure to acknowledge useful discussions with James Aird,
Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou, Xiaohui
Fan, Andrea Ferrara, Prakash Gaikwad, Martin Haehnelt, Paul Hewett,
Sergey Koposov, Donald Lynden-Bell, Roberto Maiolino, Richard McMahon,
Ewald Puchwein, Gordon Richards, Alberto Rorai, and Stephen Warren.
GK acknowledges support from ERC Advanced Grant 320596 `The Emergence
of Structure During the Epoch of Reionization'. \gk{Perhaps we need to
  specially thank people who shared data with us.  Gabor, Joe: do you
  need to add anything to acknowledgements?}

@@

In our analysis above, we did not include the 22 low-luminosity
($M_{1450}>-22.6$) AGN between redshifts $z=4.1$ and $6.3$ reported by
\citet{2015AA...578A..83G} using a novel X-ray/NIR selection
criterion.  This was because we wanted to restrict our sample to
quasars that have robust spectroscopic redshift determinations.  In
their work, \citet{2015AA...578A..83G} found a steep faint-end of the
luminosity function at these redshifts.  With this luminosity function
they obtained a large value of hydrogen ionizing emissivity that could
explain the \lya data singlehandedly.  In this section, we compare our
results with \citet{2015AA...578A..83G}.  The black points in Figure
XX show the parameters of the double power law luminosity function
when the \citet{2015AA...578A..83G} sample is added to our analysis.
The parameter values do not change significantly.  The
\citet{2015AA...578A..83G} sample is thus consistent with the double
power law luminosity function preferred by other data at comparable
redshifts.  However, as we see in Figure XX, the total emissivity in
our model is still significantly lower than that obtained by
\citet{2015AA...578A..83G}.  Figure XX provides an explanation for
this. The double power law fits favoured by \citet{2015AA...578A..83G}
are quite different from our fits.  The character luminosity $M_*$
favoured by \citet{2015AA...578A..83G} is much fainter ($\sim -23$ at
$z = 5$) than that resulting out of our analysis ($\sim -29$ at $z =
5$).  Figure XX suggests that this is because of the SDSS Stripe 82
data \gk{citation} and because \citet{2015AA...578A..83G} ignore the
Kashikawa and Willott samples \gk{citation}.  It is possible that our
corrections to the Glikman data \gk{citation} also plays a role in
this.  In sum, the differnce in our emissivities is not due to lack of
faint quasars but because of the difference with Giallongo at
intermediate luminosities.  However, our double power law fits are
virtually identical to those shown in Figure~\ref{fig:mosaic}.

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_g.pdf}
  \end{center}
  \caption{Effect of the 19 qsos reported by
    \citet{2015AA...578A..83G} on the best-fit double power law
    luminosity function parameters in redshift bins from $z=0$ to $7$.
    Black points show parameter values from Figure~\ref{fig:evoln}.
    Red open circles show the parameter values obtained when the
    sample of \citet{2015AA...578A..83G} is added to the analysis.  In
    both cases, vertical error bars show one-sigma (68.26\%)
    uncertainties, whereas horizontal error bars show widths of the
    redshift bins.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{giallongo_compare.pdf}
  \end{center}
  \caption{Luminosity functions in three redshift bins at $z>4.1$.
    Black curves in each panel show the best-fit double power law,
    with the corresponding one-sigma (68.26\%) uncertainty shown by
    the grey shaded area.  There are 451, 270, and 69 qsos in each
    redshift bin from left to right, respectively.  These numbers are
    higher than those in Figure~\ref{fig:mosaic} because they include,
    respectively, 9, 7, and 3 qsos from \citet{2015AA...578A..83G}.
    The magnitude bins containing these qsos are shown in purple.  The
    red dashed curves show the double power law fits reported by
    \citet{2015AA...578A..83G} at $z=4.25, 4.75,$ and
    $5.75$.}
\end{figure*}

@@

We make the homogenised quasar data and the code developing and
analysing luminosity function models available at
\url{https://github.com/gkulkarni/QLF} under the MIT open source
software license.  \gk{Remember to make URL public and set appropriate
  license upon publication of paper.  Add requirement of citation to
  license.}
